---
title: "Population attributable fractions"
output:
  html_document:
    df_print: paged
---

<!-- output: html_notebook -->






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


#load figures
load(here("MICS-WASH-BOD/figures/PAF_figure_objects.Rdata"))

```

We calculated population-attributable fractions (PAF):  
$$ 
PAF= \frac{p_c \times (RR_{adj}-1)}{RR_{adj}}
$$

  Which are estimates of the percent of cases in the population that could have been prevented if the whole population had their exposure shifted to a lower risk level. For example, using data from all countries, an estimated 10% of diarrhea and 14.5% of stunting could be eliminated by having improved drinking water sourced free of contimination (safely managed).

  The 95% confidence intervals (CI's) are percentile-based non-parametric, clustered bootstrap, with cluster resampling with replacement. This is why some confidence intervals are asymmetrical. Due to the computation time, PAF's have currently only been estimated for the diarrhea and stunting outcomes. PAF estimates from having improved WASH free from contamination were not calculated due to data sparsity.



```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_pooled_PAF
```

__Figure 9.__ Overall population attributable fractions (PAFs) estimated from adjusted relative risks for the binary outcomes and WASH characteristics. Instead of pooling country-specific PAF's using random-effects meta-analysis models, population attributable fractions are estimated from a dataset of all included MIC surveys, adjusting for country, due to the method of estimating confidence intervals. The confidence intervals are bootstrapped, with 100 bootstrap iterations for the presented results (the final analysis will use 1000 iterations).


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 8}
p_PAF
```

__Figure S1.__ Country-specific population attributable fractions (PAFs) estimated from adjusted relative risks for the binary outcomes and WASH characteristics. 





