---
title: "Population attributable fractions"
author: "Andrew Mertens"
output:
  html_document:
    df_print: paged
---

<!-- output: html_notebook -->






```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


#load figures


load(here("MICS-WASH-BOD/figures/PAF_figure_objects.Rdata"))
#[1] "p_PAF"        "p_pooled_PAF"

```





```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_pooled_PAF
```

__Figure 9.__ Overall population attributable fractions (PAFs) estimated from adjusted relative risks for the binary outcomes and WASH characteristics. Instead of pooling country-specific PAF's using random-effects meta-analysis models, population attributable fractions are estimated from a dataset of all included MIC surveys, adjusting for country, due to the method of estimating confidence intervals. The confidence intervals are bootstrapped, with 100 bootstrap iterations for the presented results (the final analysis will use 1000 iterations).


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 8}
p_PAF
```

__Figure S1.__ Country-specific population attributable fractions (PAFs) estimated from adjusted relative risks for the binary outcomes and WASH characteristics. 





