---
title: "Primary results"
output:
  html_document:
    toc: true  
    toc_float: true  
---

__Notes for all plots:__ Crossed points denote significant estimates at an alpha level of 0.05. Reference levels are printed under the X-axis or denoted in the plots. All presented estimates are adjusted for confounder based on the procedure outlined in the methods section. 


### Primary findings

  #. Household and source water contamination is not associated with reduced diarrhea, wasting, or mortality, and water contamination has inconsistent associations with acute respiratory infection and child stunting. The direction of point estimates across degrees of household contamination are consistent with increased risks of diarrhea, stuning, and mortality, though most estimates are not significant.

  #. Improved sanitation, hygiene, and combined WASH is associated with a decreased risk of diarrhea and stunting, and all improved WASH characteristics are associated with a decreased risk of mortality.
  
  #. Households with improved combined WASH free from contamination, when compared to households with unimproved water, sanitation, and hygiene with water contamination (the most extreme contrast) was not associated with diarrhea, stunting, wasting, or ARI's (but was associated with mortality), though this analysis suffered from data sparsity in most countries. 
  
  #. Children living in homes with very high household and source water contamination had lower HAZ, but not WHZ, compared to childrenliving in homes with no contamination.

### Limitations

  #. Unmeasured confounding is likely still present, especially when comparing results of improved WASH conditions to null results from RCT's like WASH Benefits and SHINE. There are a limited set of potential confounders to adjust for, and not all potential confounders were adjusted for in the analyses of binary outcomes that suffered from data sparsity.
  
  #. Currently, no subdivision of analyses by child age. For example, the effects of contaminated water may impact a breastfeeding child differently from an older child.





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


#load figures
load(here("MICS-WASH-BOD/figures/primary_figure_objects.Rdata"))

```




### Relative risks between measures of water contamination and binary outcomes

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3}
p_prim_pooled_WQ
```

__Figure 1. Relative risks of measures of source and household water contamination__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for the 5 binary outcomes. Panels are divided by outcome, with ARI standing for acute respiratory infection. The Y axis lists the unimproved or unsafe level of contrast, with the relative risk estimates between the improved reference level and the higher-risk level. For example, households with any level of E. coli contamination were compares to houses with uncontaminated HH water. 

### Relative risks between unimproved WASH conditions and binary outcomes

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3}
p_prim_pooled_HH
```

__Figure 2. Relative risks of unimproved WASH conditions__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for the 5 binary outcomes. The Y axis lists the unimproved or unsafe level of contrast, with the relative risk estimates between the improved reference level and the higher-risk level. For example, households with any level of E. coli contamination were compares to houses with uncontaminated HH water. Among other significant estimates, unimproved hygiene (no water and soap at handwashing station), unimproved sanitation, and unimproved combined WASH was associated with a higher risk of stunting, and unimproved combined WASH was associated with a higher risk of diarrhea, stunting, and mortality. Larger confidence intervals may represent associations estimated less precisely (e.g. for a rarer outcome like ARI) or represent heterogeneity between the country-specific estimates.

### Relative risks between levels of water contamination and binary outcomes


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_multi_pooled_WQ
```

__Figure 3. Relative risks across degrees of source and household water contamination__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for the 5 binary outcomes.  The Y axis lists the level of water contamination, with the relative risk estimates between the reference level of no contamination and the higher-risk levels. 

### Relative risks between levels of WASH service and binary outcomes


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_multi_pooled_HH
```

__Figure 4. Relative risks across levels of household WASH characteristics__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for the 5 binary outcomes.  The Y axis lists the level of WASH characteristic, with the relative risk estimates between the printed reference levels and the higher-risk levels. 

### Z-score differences between measures of water contamination


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3}
p_prim_Zscore_pooled_WQ
```

__Figure 5.  Anthropometry Z-score differences between contaminated and uncontaminated measures of source and household water__ Random-effects pooled Z-score differences, pooled  over the MICS survey countries with water quality measures, for the height-for-age Z-score (HAZ) and weight-for-height Z-scores (WHZ) outcomes. 

### Z-score differences between unimproved and improved WASH conditions


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3}
p_prim_Zscore_pooled_HH
```

__Figure 6.  Anthropometry Z-score differences between unimproved and improved measures of WASH conditions__ Random-effects pooled Z-score differences, pooled  over the MICS survey countries with water quality measures, for the height-for-age Z-score (HAZ) and weight-for-height Z-scores (WHZ) outcomes. 

### Z-score differences between levels of water contamination 

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_multi_Zscore_pooled_WQ
```

__Figure 7.  Anthropometry Z-score differences across degrees of source and household water contamination__ Random-effects pooled Z-score differences, pooled  over the MICS survey countries with water quality measures, for the height-for-age Z-score (HAZ) and weight-for-height Z-scores (WHZ) outcomes. 

### Z-score differences between levels of WASH service

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_multi_Zscore_pooled_HH
```

__Figure 8.  Anthropometry Z-score differences across levels of household WASH characteristics__ Random-effects pooled Z-score differences, pooled  over the MICS survey countries with water quality measures, for the height-for-age Z-score (HAZ) and weight-for-height Z-scores (WHZ) outcomes. 











