---
title: "Secondary results"
output:
  html_document:
  toc: true  
toc_float: true  
---
  
  __Notes for all plots:__ Crossed points denote significant estimates at an alpha level of 0.05. Reference levels are printed under the X-axis or denoted in the plots. All presented estimates are adjusted for confounder based on the procedure outlined in the methods section. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
  ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


#load figures
load(here("MICS-WASH-BOD/figures/secondary_figure_objects.Rdata"))

#load forest figures
plist <- readRDS(here("MICS-WASH-BOD/figures/forest_figure_objects.rds"))


```




### Relative risks between levels of drinking water access and diarrheal disease

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3}
p_sec_pooled

```


__Figure 11. Relative risks between levels of drinking water access conditions__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for child diarrheal disease. The Y axis lists the unimproved or unsafe level of contrast, with the relative risk estimates between the improved reference level and the higher-risk level. Note less studies are used to estimate the contrasts including water quality measurements due to sparse data.

### Relative risks between levels of sanitation access and diarrheal disease


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_sec_multi_pooled
```

__Figure 12. Relative risks across levels of household sanitation__ Random-effects pooled relative risks, pooled over MICS surveys with water quality measurements, for the 5 binary outcomes.  The Y axis lists the type and level of sanitation characteristic, with the relative risk estimates between the printed reference levels and the higher-risk levels. 



### Forest plots of levels of water access and relative risks of diarrheal disease

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}

 plist$Diarrhea.imp_off_prem_V_unimp
 plist$Diarrhea.imp_on_prem_V_imp_off_prem
 plist$Diarrhea.imp_on_prem_HQ_V_imp_on_prem_LQ
 plist$Diarrhea.imp_on_prem_sufficient_V_imp_on_prem_insufficient
 plist$Diarrhea.imp_on_prem_sufficient_HQ_V_imp_on_prem_insufficient_LQ
```

### Forest plots of levels of sanitation access and relative risks of diarrheal disease

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}

plist$Diarrhea.Piped_san_cat
 plist$Diarrhea.san_coverage
```

