---
title: "Primary figures and tables"
author: "Andrew Mertens"
output:
  html_document:
    df_print: paged
---

<!-- output: html_notebook -->
<!-- editor_options:  -->
<!--   chunk_output_type: inline -->


###To do

  *  Put saved tables after figures
  *  Adapt figure captions
  *  Put main interpretations after figures
  *  Write results section with references to figures
  *  Write limitation/open questions




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)



load(here("MICS-WASH-BOD/figures/sensitivity_figure_objects.Rdata"))


load(here("MICS-WASH-BOD/figures/mult_sensitivity_figure_objects.Rdata"))


ec_conc_figure <- readRDS(here("MICS-WASH-BOD/figures/ec-conc-figure-object.RDS"))


```



## Sensitivity analysis figures

Note: the sensitivity analysis figures are based on pooled estimated from binary codings of WASH characteristics for easier comparison between the primary and sensitivity results across the WASH conditions. Results are available for all WASH codings for all sensiivity analyses unless otherwise noted.


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_unadj_comp_RR
```


__Figure S2.__ Comparison of unadjusted and adjusted relative risks across pooled estimates and binary measures of improved WASH conditions. Unadjusted estimates are generally further from the null, indicating that covariate adjustment is correcting for some confounding between WASH conditions and child health outcomes (likely from socio-economic status as well as other factors).



```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_unadj_comp_diff
```

__Figure S3.__ Comparison of unadjusted and adjusted Z-score differences across pooled estimates and binary measures of improved WASH conditions. Unadjusted estimates are generally further from the null, indicating that covariate adjustment is correcting for some confounding between WASH conditions and child growth.

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_FE_comp_RR
```

__Figure S4.__ Comparison of random- and fixed-effects pooled relative risks across outcomes and binary measures of improved WASH conditions. Point estimates are very similiar, though random-effects estimates have larger confidence intervals when study-specific estimates are heterogeneous.

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_tmle_comp_RR
```


__Figure S5.__ Comparison of pooled relative risks of diarrhea and binary measures of household and source water contamination, estimated either with GLM and targeted maximum likelihood estimation (TMLE) models, which use ensemble machine learning models in the estimation of relative risks. The TMLE models were estimated using library with simple means, generalized linear models, generalized additive models, penalized regressions, and gradient boosting machines. 

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_tmle_comp_diff
```


__Figure S6.__ Comparison of pooled HAZ across outcomes and binary measures of improved WASH conditions, estimated either with GLM and targeted maximum likelihood estimation (TMLE) models, which use ensemble machine learning models in the estimation of relative risks. The TMLE models were estimated using library with simple means, generalized linear models, generalized additive models, penalized regressions, and gradient boosting machines. 

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_multi_pooled_HH_sens
```

__Figure S7. Relative risks across levels of household WASH characteristics, only including surveys with all levels of WASH characteristics__ The figure displays results similar to Figure 4, but only pooling estimates from surveys with sufficient observations in each level to estimate relative risks between the reference level and all contrasts.


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
p_basic
```

__Figure S8. Relative risks across levels of water and sanitation characteristics with "Basic" coded as the highest level of service__ To assess the effects of sparsity in the "high coverage" sanitation reference level and "continious" water reference level, this figure displays results of a sensitivity analysis combining the "basic" and "high coverage/continious categories" into a "basic" reference category/

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 3.5}
ec_conc_figure
```

__Figure S9.__ Curves between E. coli concentrations in source and household drinking water and child anthropometry Z-scores. Curves were estimated using generalized additive models fit to all the included MICS data.


