---
title: "Forest plots of country-specific estimates"
output:
  html_document:
    toc: true  
    toc_float: true  
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)


plist <- readRDS(here("MICS-WASH-BOD/figures/forest_figure_objects.rds"))


```



_Figure details for all plots:_ Each plot shows country-specific and pooled estimates for each WASH characteristic-outcome combination (printed in each figure title). All estimates are adjusted for potential confounders. Sample size for each estimate are in parentheses. Multi-panel figures compare categories of WASH characteristics (printed at the top of each panel) to the most-improved reference level (printed after `ref=` in the X-axis label). Points are colored by the MICS region, with pooled estimates in black, and labeled as pooled estimates from random effects (RE) or fixed effects (FE) models.


## Diarrhea {.tabset .tabset-fade .tabset-pills}

<!-- ### EC_H {.tabset .tabset-fade .tabset-pills} -->

<!-- ```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5} -->
<!--       print(plist$Diarrhea.EC_H) -->
<!-- ``` -->

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
 for(i in names(plist)){
   if(grepl("Diarrhea",i)){
       print(plist[[i]])
   }
 }
```

## Anthropometry {.tabset .tabset-fade .tabset-pills}

Click on tabs for specific anthropometry outcomes

### Stunting

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("Stunting",i))
  print(plist[[i]])
}
```

### Wasting

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("Wasting",i))
  print(plist[[i]])
}
```

### HAZ

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("HAZ",i))
  print(plist[[i]])
}
```

### WHZ

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("WHZ",i))
  print(plist[[i]])
}
```

## Acute respiratory infections

```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("ARI",i))
  print(plist[[i]])
}
```

## Mortality


```{r, echo=F, warning=F, message=F, fig.width = 10, fig.height = 5}
for(i in names(plist)){
  if(grepl("Mortality",i))
  print(plist[[i]])
}
```
