---
title: "Tables"
output:
  html_document:
    toc: true  
    toc_float: true  
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(warn = -1) 
library(janitor)
library(knitr)
library(here)
library(table1)
library(rvest)

source(here("0-config.R"))


op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
 library(pander)
panderOptions('digits', 2)
panderOptions('round', 2)
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('graph.fontsize', 8)

panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.split.table', Inf)
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)

```

## Sample details {.tabset}

```{r, echo=F, warning=F, message=F}
load(here("MICS-WASH-BOD/tables/table_objects.Rdata"))

pander(HH_tab, digits=2)

```


## WASH characteristics {.tabset}

Click on tabs for specific WASH characteristics

### Household water E. coli contamination {.tabset}

```{r, echo=F, warning=F, message=F}
pander(EC_risk_H, digits=2)
```

### Source water E. coli contamination {.tabset}

```{r, echo=F, warning=F, message=F}
pander(EC_risk_S, digits=2)
```

### Level of water supply {.tabset}

```{r, echo=F, warning=F, message=F}
pander(wat_imp_cat, digits=2)
```

### Level of sanitation {.tabset}

```{r, echo=F, warning=F, message=F}
pander(san_imp_cat, digits=2)
```

### Level of hygiene access {.tabset}

```{r, echo=F, warning=F, message=F}
pander(hyg_imp_cat, digits=2)
```

### Combined improved WASH prevalence {.tabset}

```{r, echo=F, warning=F, message=F}
pander(WASHtab, digits=2)
```



## Child health outcomes {.tabset}

Click on tabs for specific health outcomes

### Anthropometry outcomes  {.tabset}

```{r, echo=F, warning=F, message=F}
 pander(anthro_tab, digits=2)
```

### Infection and mortality outcomes  {.tabset}

```{r, echo=F, warning=F, message=F}
 pander(infection_tab, digits=2)
```




## Covariate information by country {.tabset}

```{r, echo=F, warning=F, message=F}
knitr::kable(tab1)
```

## MICS surveys used {.tabset}


```{r, echo=F, warning=F, message=F}
knitr::kable(colnames(tab1)[-c(1:2)])
```
